### 2016-02-24 Docs/managing_jobs/managingjobs.tex
some updates for SLURM edison

\begin{itemize}
\item Cray 8.4.0 works well on edison/NERSC with MPI/OpenMP

\item Intel 15.0.1 works well on edison/NERSC with MPI/OpenMP

@@

edison is configured with 24 cores per node split between two Intel
IvyBridge 12-core processors.  Each processor connects to 1/2 of the
node's memory and is called a NUMA node, so there are 2 NUMA nodes per
edison node.  Best performance is seen when running with 6 or 12 threads.
\begin{verbatim}
aprun -n 192 -N 4 -S 2 -d 6 ./main.Linux.Cray.mpi.omp.exe inputs_3d
\end{verbatim}
Here,
\begin{itemize}
\item {\tt -S} is the number of MPI tasks per NUMA node (you want to split them
  across the 2 NUMA nodes per Edison node)
\item {\tt -n} is the total number of MPI tasks for the entire application
\item {\tt -N} is the number of MPI tasks PER Edison node
\item {\tt -d} is the number of OpenMP threads per MPI task (must match 
{\tt OMP\_NUM\_THREADS})
\end{itemize}
The product of {\tt -N} and {\tt -d} should be 24---the total number of cores
per edison node.
The script {\tt
Util/job\_scripts/edison/edison.run} provides an example.

Note that with the Intel compilers, you should never use the {\tt -ss}
option to {\tt aprun}, and should use {\tt -cc depth} for $< 12$
threads and {\tt -cc numa\_node} for $12$ threads.

>>>>

\begin{itemize}
\item Intel 15.0.1 works well on edison/NERSC with MPI/OpenMP

\item Cray 8.4.3 triggers a backtrace error in {\tt make\_pi\_cc.f90}---this is 
  likely an optimization issue, and may be 2-d specific.

  Previously,  Cray 8.4.0 worked well on edison/NERSC with MPI/OpenMP.

@@

edison is configured with 24 cores per node split between two Intel
IvyBridge 12-core processors.  Each processor connects to 1/2 of the
node's memory and is called a NUMA node, so there are 2 NUMA nodes per
edison node.  Best performance is seen when running with 6 or 12 threads.

Note: edison switched to SLURM as the batch system.  Your job is submitted
using the {\tt sbatch} command.  Options to {\tt sbatch} are specified at the
top of your submission script with {\tt \#SBATCH} as the prefix.  These options
can be found on the {\tt sbatch manpage}.  For instance, 
\begin{verbatim}
#SBATCH -N 2
#SBATCH -J myjob
#SBATCH -A repo-name
#SBATCH -p regular
#SBATCH -t 12:00:00
\end{verbatim}
will request 2 nodes ({\tt -N}), under the account {\tt repo-name} ({\tt -J}),
in the regular queue, and for a 12-hour window {\tt -t}.

If you are using OpenMP, then your script should set {\tt OMP\_NUM\_THREADS}, e.g.,
\begin{verbatim}
export OMP_NUM_THREADS=12
\end{verbatim}

By default, SLURM will change directory into the submission directory.  The 
job is launched from your script using {\tt srun}, e.g.:
\begin{verbatim}
srun -n 48 ./main.Linux.Cray.mpi.exe inputs_3d
\end{verbatim}
to run 48 MPI tasks (across the 2 nodes), or 
\begin{verbatim}
export OMP_NUM_THREADS=6
srun -n 8 -c 6 ./main.Linux.Cray.mpi.omp.exe inputs_3d
\end{verbatim}
to use 8 MPI tasks each with 6 threads.

The scripts in {\tt Util/job\_scripts/edison/} provides some examples.

{\em Not sure if this still applies: Note that with the Intel compilers, you should never use the {\tt -ss}
option to {\tt aprun}, and should use {\tt -cc depth} for $< 12$
threads and {\tt -cc numa\_node} for $12$ threads.}
